\documentclass[conference]{IEEEtran}

\usepackage{verbatim}	%Multi line comment using \begin{comment} and \end{comment)

\title{802.11p Literature Review and Attacks}
\author{\IEEEauthorblockN{Aniket Chaudhari and Alvin Cai and Wouter de Groot and Erik Schneider}
\IEEEauthorblockA{Technische Universiteit Eindhoven\\
Eindhoven, The Netherlands\\
\\
September 30, 2014}}

\begin{document}
\maketitle

\begin{abstract}
In this literature review, we describe 802.11p, 1609.2 and attacks on vehicular networks in the context of “Security and Privacy in Mobile Systems”.
\end{abstract}

\section{Introduction}

\begin{comment}
I think we should amend the first paragraph to provide an overview of VANET in general before jumping into 802.11p.

I made some amendments to para 2 and 3, to align to the modified scope. i.e. 
a) The literature review is the main meat of this project
b) It must provide a comprehensive survey of different attacks 
c) We can explain the attacks we want to implement in more detail
d) Focus on attacks in OSI layer 1-3
\end{comment}

Communications and netwoking are key factors in the development of an intelligent transportation systems which aims to automate the interactions among vehicles and infrastructure to achieve high levels of safety, efficiency and comfort. The IEEE has developed a system architecture known as wireless access in vehicular networks (WAVE) which comprises the IEEE 802.1p and IEEE 1609.x standards.

802.11p is an amendment to the 802.11 wireless communication standard specifically designed for vehicle to vehicle communication mainly related to safety issues such as warning of incidents. It utilizes the 5.9 GHz frequency band and is designed to accommodate very short-lived communication links. 802.11p is a PHY and MAC layer standards. The IEEE 1609 family of standards are a set of higher layer protocols which aims to address other issues such as security and efficient routing protocols.\\

In this paper we will provide a literature review of 802.11p, the security component of IEEE 1609 and provide an overview of vehicular network attacks targeted at the OSI layers of 1, 2 and 3. This survey will inform our choice of attacks to implement during the practical phase of the project. In addition, we will attempt to demonstrate new attacks through the implementation of a fuzzing framework.

\section{Wave Architecture}
\input{wave}


\section{Attacks}
Aijaz et al. \cite{aijaz2006attacks} employ attack trees to assess the vehicular communication threat model and provides a useful classification system for both existing and future attacks. 

We will describe the main attacks proposed and evaluate if the current standard are vulnerable to these attack. 



\subsection{PHY Layer}
\input{layer1}

\subsection{MAC Layer}
\input{layer2}



\subsection{Network Layer}
\input{layer3}


\section{Methodology}
\subsection{ Implementations of Existing Attacks}
\label{sec:existing_attacks}
Ath5k is a common open source driver for Qualcomm Atheros based wireless chipsets in Linux and will be the focus for replicating existing attacks. Specifically, we will interface with the drivers for the packets in packets attack and modify the drivers for the DOS attack. We will then evaluate if the 802.11p reference devices (available at Twente) or Atheros drivers are vulnerable. If the drivers are vulnerable, we will attempt to propose a fix and evaluate the efficacy of this fix.\\

\subsection{Fuzzing Framework}
\input{fuzz}

\section{Results}
This section will contain a list of exploits discovered as a result of our fuzzing. For each flaw, we will detail the method and the potential consequences of its exploitation.

\section{Analysis}
This section may be merged with Results if we discover a novel attack. Otherwise, this section will analyze the strength and limitations of our approach.

\section{Discussion}
This section will provide a critical assessment of the current research into 802.11p security, including our contributions. Among the lines of analysis to be considered are the following questions: How did our work contribute to the state of the art? What are the consequences for 802.11p? What are the most promising avenues of research? What are the limitations in our research?

\bibliographystyle{IEEEtran}
\bibliography{Skeleton.bib}

\end{document}